Project Report

### 2021-04-30 report/paper.tex
Add to report

The specification is typically given in the form of a transition system (consisting of states and \emph{actions} which give rise to transitions between states) and invariants. A model checker may then be used to output sequences of states which violate the invariants. Such sequences may equivalently be seen as sequences of actions, starting and ending at particular states.

@@

\begin{enumerate}
\item An abstraction function, mapping an implementation state to a specification state.
\item An interpreter for actions. In some sense this may be seen as a concretization function, mapping a specification action to an implementation state change, as well as a means for effecting said state change.
\end{enumerate}

@@

\begin{itemize}
\item \textbf{Concurrency.} The interpreter has to drive the implementation forward in such a way that each intermediate state corresponds to a linearization point. There is otherwise no guarantee that any observed implementation state matches some specification state. To ensure this, the interpreter is synchronised, e.g. waiting for a message to appear in the soup as confirmation that an action has executed. At that point we know that the system is relatively quiescent and can observe its state.

\item \textbf{Modifications.} Implementing the interpreter might require changes to the implementation which interfere with its integrity: to what extent is the modified implementation representative of the program we want to check the conformance of? For this to work the implementation must natively support the interpretation of actions. This is of particular concern when the interpreter is retroactively added to an implementation, as we are doing. To deal with this, we try to limit our changes to events that may be externally controlled, e.g. timeouts and message sends and receives, and implement only what is necessary to expose external control of such events.

@@

\item \textbf{Nondeterminism.} Nondeterministic specification actions typically correspond to some composition of implementation actions with a deterministic prefix. For example, a specification action might require that a message is sent when a variable has a certain value; an implementation is likely to send this message upon the variable's value changing as part of an earlier action. Decoupling these actions in the implementation is not always possible (if determinism is required) or desirable (if it would be a nontrivial implementation change). Not decoupling them would run the risk of the linearization point being misplaced, but we choose this option instead, with a number of mitigating measures:

@@

>>>>

The specification is typically given in the form of a transition system (consisting of states and \emph{actions} which give rise to transitions between states) and its invariants. A model checker may then be used to output sequences of states which violate the invariants. Such sequences may equivalently be seen as sequences of actions, starting and ending at particular states.

@@

\begin{enumerate}
\item An abstraction function, mapping an implementation state to a specification state.
\item An interpreter for actions. In some sense this may be seen as a concretization function, mapping a specification action to an implementation state change.
\end{enumerate}

@@

\begin{itemize}
\item \textbf{Concurrency.} The interpreter has to drive the implementation forward in such a way that each intermediate state corresponds to a linearization point. There is otherwise no guarantee that any observed implementation state matches some specification state. To ensure this, the interpreter is synchronised, e.g. waiting for a message to appear in the soup as confirmation that an action has been executed. At that point we know that the system is relatively quiescent and can observe its state.

\item \textbf{Modifications.} Implementing the interpreter might require changes to the implementation which interfere with its integrity: to what extent is the modified implementation representative of the program we want to check the conformance of? This is of particular concern when the interpreter is retroactively added to an implementation, as we are doing; ideally, the implementation would natively support interpreting actions. We try to minimize our changes and limit them to events that may be externally controlled, e.g. timeouts and message sends and receives, and implement only what is necessary to expose external control of such events.

@@

\item \textbf{Nondeterminism.} Nondeterministic specification actions typically correspond to some composition of implementation actions with a deterministic prefix. For example, a specification action might require that a message is sent when a variable has a certain value; an implementation is likely to send this message upon the variable's value changing as part of an earlier action. Decoupling these actions in the implementation is not always possible (if determinism is required) or desirable (if it would be a nontrivial implementation change). Not decoupling them would risk the linearization point being misplaced, but we choose this option instead, with a number of mitigating measures:

@@

% manual work required to create a test case:

% - manually removed messages nodes send to themselves (there's no analogue in the impl)
% - extra action manually added at the end, to ensure that we've waited long enough for the state to quiesce before inspecting it
% - the subparts of the spec and impl state that we want to compare need to be defined for each kind of test
